%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-8pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-4pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-10pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-8pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Large \scshape Sai Siddharth Cilamkoti} \\ \vspace{1pt}
    \small +1-716-808-4577 $|$ \href{mailto:siddharthcilamkoti@gmail.com}{\underline{siddharthcilamkoti@gmail.com}} $|$ 
    \href{https://linkedin.com/in/sai-siddharth-cilamkoti/}{\underline{linkedin.com/in/sai-siddharth-cilamkoti}} $|$
    \href{https://github.com/siddharthc30}{\underline{github.com/siddharthc30}} $|$
    \href{https://siddharthc30.github.io/}{\underline{siddharthc30.github.io}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University at Buffalo}{Buffalo, New York}
      {Master of Science in Computer Science}{Aug. 2023 -- May 2025}
      \resumeItemListStart
        \resumeItem{Concentration: Machine Learning and Artificial Intelligence}
        \resumeItem{Relevant Courses: Data Structures \& Algorithms, Operating Systems, Machine Learning, Deep Learning}
      \resumeItemListEnd
    \resumeSubheading
      {Amrita Vishwa Vidyapeetham}{India}
      {Bachelor of Technology in Computer Science with AI}{Aug. 2019 -- May 2023}
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming}{: Python, Java, SQL, Javascript, C++, HTML/CSS} \\
     \textbf{AI \& ML}{: PyTorch, LangChain, LangGraph, VectorDBs, Sklearn, NumPy, Huggingface, Fine-Tuning, Prompt Engineering, RAG, AWS Bedrock, Gemini, Anthropic, OpenAI API} \\
     \textbf{Backend \& API}{: Spring Boot, FastAPI, Flask, WebSockets, Microservices}  \\
    \textbf{DevOps and Tools}{: Docker, GitHub Actions, AWS, Azure Dev Tools, Git, Linux, Cursor}
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Associate AI Engineer}{Nov 2025 -- Mar. 2026}
      {Midwest Partners LLC}{Remote}
      \resumeItemListStart
        \resumeItem{Built a competitor price tracking pipeline using n8n, SerpAPI (Google Hotels API), and Supabase Postgres to monitor rates across multiple hotels at regular intervals in real time.}
        \resumeItem{Designed a scheduling + alerting workflow that detects when the client's pricing exceeds competitors and fires Slack/email notifications directly tied to Google metasearch ranking signals.}
        \resumeItem{Integrated Google Places API for review monitoring and sentiment tracking across Google, TripAdvisor, and OTA platforms.}
      \resumeItemListEnd
      
     \resumeSubheading
      {Research AI Engineer}{Feb. 2024 -- Aug 2025}
      {University at Buffalo}{Buffalo, New York}
      \resumeItemListStart
        \resumeItem{Engineered a Distributed System evaluation pipeline for large-scale code generation, automating telemetry tracking and execution across 1,000+ distinct test cases.}
        \resumeItem{Implemented parallel execution strategies using Python to optimize runtime efficiency, building ETL workflows to collect, transform, and pipeline server-side telemetry data monitoring resource utilization across distributed nodes to identify optimal performance-to-cost configurations.}
        \resumeItem{Devised backend optimization strategies (Quantization/Pruning) for high-load systems, achieving a 20\% reduction in server energy consumption while maintaining system integrity.}
        \resumeItem{Contributed technical documentation and system analysis accepted for publication at FLLM 2025, focusing on infrastructure performance metrics.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{Aug. 2024 -- Dec. 2024}
      {Kaleida Health}{Buffalo, New York}
      \resumeItemListStart
        \resumeItem{Architected a scalable Microservices Architecture for a full-stack healthcare platform using Java Spring Boot and React, deploying to AWS infrastructure to ensure high availability for hospital operations.}
        \resumeItem{Developed a custom RAG-based AI-powered QA chatbot using LangChain and LangGraph, orchestrating workflows with conversation memory to enable patients to interactively query information about their diagnosed conditions.}
        \resumeItem{Indexed verified medical documentation into Amazon OpenSearch as the vector store, with embeddings generated via Amazon Bedrock and inference served through AWS Lambda and Amazon API Gateway; evaluated end-to-end pipeline quality using the RAGAs framework and monitored production traces and token usage via LangSmith for full observability.}
        \resumeItem{Engineered secure RESTful APIs and integrated WebSockets to support real-time, low-latency communication, successfully handling high volumes of concurrent connections with automatic translation of messages based on preferred languages.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Plant Disease Detection with Chatbot Support} $|$ \emph{Python, PyTorch, LangChain, Gradio}}{\href{https://github.com/siddharthc30/Early-Plant-Disease-Detection}{\underline{GitHub}} $|$ 2024}
          \resumeItemListStart
            \resumeItem{Developed an AI system utilizing advanced computer vision techniques and fine tuned a VGG model to rapidly identify early-stage plant diseases through detailed leaf image analysis achieving a 92\% accuracy.}
            \resumeItem{Integrated OpenAI's DaVinci LLM via LangChain to generate context-aware plant management advice for effective plant management and disease prevention strategies.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Review Analyzer} $|$ \emph{Python, Flask, Azure Cognitive Services, REST API}}{\href{https://github.com/siddharthc30/ReviewGenie}{\underline{GitHub}} $|$ 2023}
          \resumeItemListStart
            \resumeItem{Engineered an ML-driven decision-support tool to analyze reviews and extract sentiment patterns for Amazon purchasing choices.}
            \resumeItem{Built a full-stack Flask application integrating Azure Cognitive Services, structured JSON APIs, and secure cloud-based inference endpoints.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd





%-------------------------------------------
\end{document}
